\documentclass[11pt]{article}

\pagestyle{empty}                       %no page numbers
\thispagestyle{empty}                   %removes first page number
\setlength{\parindent}{0in}               %no paragraph indents

\usepackage{fullpage}
\usepackage[tmargin = 0.5in, bmargin = 1in, hmargin = 1in]{geometry}     %1-inch margins
\geometry{letterpaper}                  
\usepackage{graphicx}
\usepackage{amssymb}

% Default packages
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{palatino}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{enumitem}

\def\pageturn{\vfill
\begin{flushright}
	\begin{small}
		Continued $\rightarrow$
	\end{small}
\end{flushright}
\newpage}

\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}


\def\ra{\rightarrow}

\begin{document}
	
	\thispagestyle{empty}
	\renewcommand{\headrulewidth}{0.0pt}
	\thispagestyle{fancy}
	\lhead{Prof. Talbert}
	\chead{MTH 210: Communicating in Mathematics}
	\rhead{October 19, 2012}
	\lfoot{}
	\cfoot{}
	\rfoot{}	
	
	\vspace*{0in}

		\begin{center}
			\begin{large}
			\textbf{Class Work: Proving Set Relationships} \\
			\end{large}
			This is a full-time activity worth 10 points. 
			
		\end{center}
		

\section*{Problems of the Day}

Give complete proofs for ALL of the statements below. Some of these are very short. You will submit this proof in a formal writeup at the end of the class. For all of these statements, $A$ and $B$ are sets that are subsets of some universal set $U$. 

\begin{enumerate}
	\item Prove BOTH of the following. They should be very short. 
	\begin{enumerate}
		\item Prove $A \cap B \subseteq A$. 
		\item Prove $A \subseteq A \cup B$.
	\end{enumerate}
	\item Prove ONE of the following. These are not as short. 
	\begin{enumerate}
		\item Prove that if $A \subseteq B$, then $A \cap C \subseteq B \cap C$. 
		\item Prove that if $A \subseteq B$, then $A \cup C \subseteq B \cup C$. 
	\end{enumerate}
	\item Prove ONE of the following. 
	\begin{enumerate}
		\item Prove that the sets $A \cap B$ and $A - B$ are disjoint. 
		\item Prove that $A - B = A \cap B^c$. 
	\end{enumerate}
	
	 
	
\end{enumerate}

\section*{Parameters}

If your group finishes the proof you're assigned, please hand it in at the end of class. If all groups finish by the end of class, we will take time to debrief the solutions to one or more of these. 

\end{document}